Probabilistic Catalogs from Crowded Star Fields

### 2012-07-16 paper/ms.tex
More writing

\subsection{The Sampling Distribution}

\subsection{The Prior Distribution}

{Simulated Data}

A model for the spatial distribution corresponds to a choice of functional
forms for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:

@@

>>>>

\subsection{The Sampling Distribution}
The sampling distribution is a probabilistic model for the process that
generates the data. {\bf PSF and Gaussian Noise}

\subsection{The Prior Distribution}
A model for the spatial distribution corresponds to a choice of functional
forms for the distributions $p(x_i, y_i | \alpha)$ and $p(f_i | \beta)$.

\section{Three Scenarios: Sparse, Cluster, and Crowded}
In this paper we discuss three test cases, named \sparse, \cluster
and \crowded. For the generation of the simulated
images, we used the following assumptions:

@@

\subsection{Sparse}
Sparse has a giant first-order phase transition. {\bf Nested Sampling is
mandatory!} Show the plot of it

\subsection{Cluster}
Was generated from non-uniform spatial distribution (obviously) but modelled
with a uniform one.

\subsection{Crowded}
Crowded is slow if the data have high S/N. Something like $e^5000$ compressions
are needed. Can do NS and not worry about equilibration if you are willing to
make a guess about the logXs of the levels.
